---
title: "9120hw3"
author: "Ze Li"
output: pdf_document
---

```{r library, message=FALSE}
# knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(Matrix)
library(glmnet)
library(keras)
library(jpeg)
library(tidyverse)
library(ggthemes)
library(tensorflow)
```

```{r}
library(tensorflow)
use_condaenv("base", required = TRUE)
install_tensorflow()
library(keras)
```


## Question 3. Exercise 8 (Section 10.10) of [ISL Python version] 

Pick pick 10 images of animals (such as dogs, cats, birds, farm animals, etc.). If the subject does not occupy a reasonable part of the image, then crop the image. Now use a pretrained image classification CNN as in Lab 10.9.4 to predict the class of each of your images, and report the probabilities for the top five predicted classes for each image.

```{r pretrained CNN model}
img_dir <- "images"
image_names <- list.files(img_dir)
image_names
num_images <- length(image_names)
x <- array(dim = c(num_images, 224, 224, 3)) 

for (i in 1:num_images) {
  img_path <- paste(img_dir, image_names[i], sep = "/") 
  img <- keras::image_load(img_path, grayscale = FALSE, color_mode="rgb", target_size = c(224, 224), interpolation = "nearest")
  x[i,,, ] <- image_to_array(img)
}
```

```{r 10 images}
par(mar = c(0, 0, 0, 0), mfrow = c(2, 5))
x_temp <- x / 255
for (i in 1:10) plot(as.raster(x_temp[i,,, ]))
x <- imagenet_preprocess_input(x)
model <- application_resnet50(weights = "imagenet") 
summary(model)
```

```{r}
pred10 <- model %>% predict(x) %>%
  imagenet_decode_predictions(top = 5) 
names(pred10) <- image_names
print(pred10)
```

